\plaintitle

### 2018-04-01 paper/paper.tex
...

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
% \usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}

@@

\numberofauthors{3}
\author{%
%  \alignauthor{Leave Authors Anonymous\\
%    \affaddr{for Submission}\\
%    \affaddr{City, Country}\\
%    \email{e-mail address}}\\
  \alignauthor{Toshiyuki Masui
    \affaddr{Keio University}\\
    \affaddr{Fujisawa, Japan}\\
    \email{masui@pitecan.com}}\\
  \alignauthor{Jun Kato\\
    \affaddr{AIST}\\
    \affaddr{Tsukuba, Japan}\\
    \email{junkato}}\\
}

@@

We propose a command translation system with which users can get a complete
command string

@@

We have implemented ``GitHtlp'' that

>>>>

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
% \usepackage[pdflang={en-US},pdftex]{hyperref} なんかわからない
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}

@@

\numberofauthors{3}
\author{%
  \alignauthor{Toshiyuki Masui
    \affaddr{Keio University}\\
    \affaddr{Fujisawa, Japan}\\
    \email{masui@pitecan.com}}\\
  \alignauthor{Jun Kato\\
    \affaddr{AIST}\\
    \affaddr{Tsukuba, Japan}\\
    \email{junkato}}\\
}

@@

We propose a command translation system with which users can generate a complete
command string.
%
We provide a database consisting of
pairs of
(1) the description of the task that users want to perform,
and
(2) the actual command string required by the system.
(1) can be written using regular expressions in any language,

For example, the database can include data like
\texttt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.

@@

We have implemented the ``GitHtlp'' system that can translate
user' intentions into a correct \texttt{git} commands
using the \textsf{ExpandHelp} framework.

\paragraph{Entering a command}

We assume that a user is using \texttt{bash} for developing a software system.

When a

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
  \caption{Bash shell.}
  \label{bash1}
\end{figure}

When the user wants to compare the latest \texttt{README.md} file with an
older version, he tries to use \texttt{git} to show the difference.
He may know that he can use the \texttt{git diff} command to do the
conparison and invoke the following command,

\begin{quotation}
  \verb|$ git diff README.md|
\end{quotation}

but nothing happens, because this is not the right command
to compare the latest version with older version.
%
More experienced user might use a command like the following,
but it does not show anything either, because
\verb|HEAD^^| means...

\begin{quotation}
  \verb|$ git diff HEAD^^ README.md|
\end{quotation}

Instead, the user can type \texttt{Cmd-Ctrl-G} to invoke
\textsf{GitHelp}
after typing
\texttt{\$ git RE 2}.

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 1290 866]{figures/githelp1.png}
  \caption{Invoking GitHelp.}
  \label{bash1}
\end{figure}

Here, various command strings and descriptions are listed,
one of which says ``.....'',
which means that ``to compare README with two older verson.''
%
If the user thinks that that's what he wanted to do,
he can select the entry by typing arrow keys and
type the enter key.
